Accurate evaluation of dislocation tractions

### 2021-01-13 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Break for eating.

Things get markedly more interesting when looking at $\vec{b} = \vec{b}_{\textrm{e2}}$ in \cref{f:head_vs_ana_vs_num_epar}. Of particular note is $\hat{\sigma}_{xx}$, where a comparison between \cref{sf:sxxepar,sf:sxxAepar} and \cref{sf:sxxNepar} reveals one of the major issues with numeric tractions. If we look at the neighbourhood of the dislocation (just to the right), we will find a sign inversion (yellow and green contours as opposed to purple and blue) as well as a drastically different isosurface shape Here the isolines are not merely deformed nor pinched in the way that is indicative of numerical artifacting. They are fundamentally different when calculated with numeric tractions. Image stresses like those can lead dislocations to behave differently than they should, particularly if the sign inversion also comes with an increased force magnitude, which judging from \cref{f:rel_err_par_edge} is quite possible. Specifically, there is a region in the positive $x$-direction away from the dislocation where $\hat{\sigma}_{xx}$ is tensile rather than compressive. It is as absurd as a ship inverts the Archimidean principle. The other two stress fields $\hat{\sigma}_{yy}$, $\hat{\sigma}_{xy}$ follow similar trends to what we have already observed, where the isolines get squashed and flair towards the traction free surface.
\begin{figure}
    \centering
    \subfloat[%$\hat{\sigma}_{xx}$.
        \label{sf:sxxepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxEpar.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
        \label{sf:sxxAepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxAEpar.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
        \label{sf:sxxNepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxxNEpar.pdf}}
    }

    \subfloat[%$\hat{\sigma}_{yy}$.
        \label{sf:syyepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyEpar.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
        \label{sf:syyAepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyAEpar.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
        \label{sf:syyNepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syyNEpar.pdf}}
    }

    \subfloat[%$\hat{\sigma}_{xy}$.
        \label{sf:sxyepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyEpar.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
        \label{sf:sxyAepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyAEpar.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
        \label{sf:sxyNepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxyNEpar.pdf}}
    }
    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$, where $a = 5~b$, with coordinates $(25.6410,\, 1000)~b$, i.e. the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom. From left to right, the subfigure columns correspond to the stress fields for the infinite-domain solution (no superscript), analytic tractions + FEM (A superscript), and numeric tractions ($Q = 1$) + FEM (N superscript). The subfigure rows from top to bottom represent $\hat{\sigma}_{xx}$, $\hat{\sigma}_{yy}$ and $\hat{\sigma}_{xy}$.}
    \label{f:head_vs_ana_vs_num_epar}
\end{figure}

>>>>

Things get markedly more interesting when looking at $\vec{b} = \vec{b}_{\textrm{e2}}$ in \cref{f:head_vs_ana_vs_num_epar}. Of particular note is $\hat{\sigma}_{xx}$, where a comparison between \cref{sf:sxxepar,sf:sxxAepar} and \cref{sf:sxxNepar} reveals one of the major issues with numeric tractions. If we look at the neighbourhood of the dislocation (just to the right), we will find a sign inversion (yellow and green contours as opposed to purple and blue) as well as a drastically different isosurface shape Here the isolines are not merely deformed nor pinched in the way that is indicative of numerical artifacting. They are fundamentally different when calculated with numeric tractions. Image stresses like those can lead dislocations to behave differently than they should, particularly if the sign inversion also comes with an increased force magnitude, which judging from \cref{f:rel_err_par_edge} is quite possible. Specifically, there is a region in the positive $x$-direction away from the dislocation where $\hat{\sigma}_{xx}$ is tensile rather than compressive. It is as absurd as a ship inverts the Archimidean principle. The other two stress fields $\hat{\sigma}_{yy}$, $\hat{\sigma}_{xy}$ follow similar trends to what we have already observed, where the isolines get squashed and flair towards the traction free surface.
\begin{figure}
    \centering
    \subfloat[%$\hat{\sigma}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxAepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxAEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxNepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxNEpar_leg.pdf}}
    }~
    \subfloat{
        \includegraphics[height = 0.22\linewidth]{sxxNAEpar_leg.pdf}
    }

    \subfloat[%$\hat{\sigma}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syyEpar.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyAepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syyAEpar.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyNepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syyNEpar.pdf}}
    }

    \subfloat[%$\hat{\sigma}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxyEpar.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyAepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxyAEpar.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyNepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxyNEpar.pdf}}
    }
    \caption{Image stresses for an edge dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 1 0]$, where $a = 5~b$, with coordinates $(25.6410,\, 1000)~b$, i.e. the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom. From left to right, the subfigure columns correspond to the stress fields for the infinite-domain solution (no superscript), analytic tractions + FEM (A superscript), and numeric tractions ($Q = 1$) + FEM (N superscript). The subfigure rows from top to bottom represent $\hat{\sigma}_{xx}$, $\hat{\sigma}_{yy}$ and $\hat{\sigma}_{xy}$.}
    \label{f:head_vs_ana_vs_num_epar}
\end{figure}
